gtsummary Reviewer Responses

### 2021-04-13 reviewer_responses/gtsummary_review_2021-03-23.Rmd
small updates

> The reviewer raises a great point. One of the great features of gtsummary is teh accessabitily of every gt function to produce a highly customized table, when needed. We have included functions to assist in common formatting to make them more accessible to users. For example, to re-created the functionality of the `bold_labels()` function, the user would need to pass `as_gt() %>% gt::tab_style(style = gt::cell_text(weight = "bold"), locations = gt::cells_body(columns = gt::vars(label), rows = row_type == "label"))`. The helper function is much easier to read, and moreover, the gt version requires knowledge of hidden columns (e.g. `"row_type"`) to correctly select the label rows. Without these formatting helper functions, most passive users of the package would not have the knowledge to create the formatting on their own.

@@

> The ordering of the variable in `tbl_summary()` aligns with the order the variables appear in the input data frame. To re-arrange the variables, use `select()` before passing the data frame to `tbl_summary()`, e.g. `trial %>% select(age, grade) %>% tbl_summary()`

@@

> Yes! Any function in base R, another package, or user-defined can be used to summarize the continuos data in `tbl_summary()`. The only restriction is the first argument of the function must accept a vector, and return a scalar.

@@

> The terms appear in the same order as regression function. The simplest way to reorder the terms to order them in, for example, the `lm()` call. If for some reason that is not possible, they can be re-ordered after the `tbl_regression()` table has been built using `modify_table_body()` with `dplyr::arrange()`.

>>>>

> The reviewer raises a great point. One of the great features of gtsummary is the accessibility of every gt function to produce a highly customized table, when needed. We have included functions to assist in common formatting to make them more accessible to users. For example, to re-created the functionality of the `bold_labels()` function, the user would need to pass `as_gt() %>% gt::tab_style(style = gt::cell_text(weight = "bold"), locations = gt::cells_body(columns = gt::vars(label), rows = row_type == "label"))`. The helper function is much easier to read, and moreover, the gt version requires knowledge of hidden columns (e.g. `"row_type"`) to correctly select the label rows. Without these formatting helper functions, most passive users of the package would not have the knowledge to create the formatting on their own.

@@

> The ordering of the variable in `tbl_summary()` aligns with the order the variables appear in the input data frame. To re-arrange the variables, use `select()` before passing the data frame to `tbl_summary()`, e.g. `trial %>% select(age, grade) %>% tbl_summary()`. Custom ordering of categorical variable levels can be done manually, or using forcats convenience functions (e.g. `forcats:fct_relevel()`) before passing data.

@@

> Yes! Any function in base R, another package, or user-defined can be used to summarize the continuous data in `tbl_summary()`. The only restriction is the first argument of the function must accept a vector and return a scalar.

@@

> The terms appear in the same order as in regression function. The simplest way to reorder the terms is to order them directly in call, for example, in the `lm()` call. If for some reason that is not possible, they can be re-ordered after the `tbl_regression()` table has been built using `modify_table_body()` with `dplyr::arrange()`.
